### 2016-08-31 version0.0/paper1.tex
Adding an appendix about Bayesian fitting

We found the free parameters by applying the hierarchical Bayesian linear regression method as described in \citet{Shetty13}. Shetty and colleagues used a Bayesian linear regression approach in a new method to find the K-S law parameters, considering the measurement uncertainties as well as hierarchical data structure.
We used the same technique as \citet{Shetty13} to estimate the K-S law parameters. For the extended Schmidt law, we extended the code such that instead of using  simple hierarchical Bayesian linear regression, which is used for the K-S law, it uses multiple hierarchical Bayesian linear regression. In this case, we were able to examine the effect of stellar mass on the SFR as shown in equation~\ref{eq:sfr_law_es_log}.

@@

\begin{figure}
        \centering
        \includegraphics[width=\textwidth]{../image_paper1/es_tot_fuv_vs_tot2_f.png}
        \caption[Result from fitting the extended Schmidt law on the M31 data of the whole galaxy]{The result from fitting the extended Schmidt law on the surface density of SFR(FUV + 24~$\mu$m), the surface density of total gas and the surface density of stellar mass ($z$-axis) from the whole galaxy. Solid line shows the best fit (the mean value of the range reported in Table~\ref{table:res}) from a pixel-by-pixel method. Equivalent plots for the other SFR and gas tracers are in Fig.s~\ref{fig:es,all,fir,h2} - ~\ref{fig:es,all,halpha,tot} in the appendix.}
        \label{fig:es,all,fuv,tot}
    \end{figure}

>>>>

We found the free parameters by applying the hierarchical Bayesian linear regression method as described in \citet{Shetty13}. Shetty and colleagues used a Bayesian linear regression approach in a new method to find the K-S law parameters, considering the measurement uncertainties as well as hierarchical data structure (for more detail on fitting procedure see Appendix~\ref{app:bays_fitting}).
We used the same technique as \citet{Shetty13} to estimate the K-S law parameters. For the extended Schmidt law, we extended the code such that instead of using simple hierarchical Bayesian linear regression, which is used for the K-S law, it uses multiple hierarchical Bayesian linear regression. In this case, we were able to examine the effect of stellar mass on the SFR as shown in equation~\ref{eq:sfr_law_es_log}.

@@

\begin{figure}
        \centering
        \includegraphics[width=\textwidth]{../image_paper1/es_tot_fuv_vs_tot2_f.png}
        \caption[Result from fitting the extended Schmidt law on the M31 data of the whole galaxy]{The result from fitting the extended Schmidt law on the surface density of SFR(FUV + 24~$\mu$m), the surface density of total gas and the surface density of stellar mass ($z$-axis) from the whole galaxy. Solid line shows the best fit (the mean value of the range reported in Table~\ref{table:res}) from a pixel-by-pixel method. Equivalent plots for the other SFR and gas tracers are in Fig.s~\ref{fig:es,all,fir,h2} - ~\ref{fig:es,all,halpha,tot} in the Appendix~\ref{app:es,figs}.}
        \label{fig:es,all,fuv,tot}
    \end{figure}
